Water desalination using polyelectrolyte hydrogel. Gibbs ensemble modelling

### 2022-07-05 gibbs.tex
added W_sim to the table

%Let $\nna$ and $\ncl$ be the density of the corresponding ion in the compression volume, $\Vbox$ averaged over this volume
\begin{equation}
N_i = N_i\gel + \cs\cdot(\Vbox - \Vgel)
\end{equation}
where $i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel,

@@

\paragraph{Closed system.}
The similar scheme we use to simulate the gel in closed system. 
The procedure represents a chain of subsequent MD and MC simulation, but now the molecular dynamics is runing in two simulation boxes simultaneously.
The first box of the volume $\Vgel$ contains the gel with ions, and the second box, $\Vout$--- contains only ions. 
The total volume of both boxes is kept constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the compression of the gel implies the decreasing $\Vgel$ and increasing $\Vout$.
These two boxes are represented in \reffig{fig:diamond}.

\paragraph{Algorithm.}
The thermodynamic equilibrium between the two volumes implies the exchange of the ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
The simulation algorithm is following:
\begin{enumerate}
\item Simulate molecular dynamics in both boxes; collect the observables, for examples, values of pressure $P$, to an array; 
\item Perform Monte-Carlo procedure simulating ion pair exchange; collect the arrays of observables samples: number of ions in both boxes, $\nna\gel$,
$\ncl\gel$, $\nna\out$ and $\ncl\out$ ; 
\item Repeat the procedure until the desired length of sample arrays is reached.
\end{enumerate}

@@

The dependencies of $\Pgel$ on the gel molar volume $\Vgel$ are present in Figure \ref{fig: PV} for a set of different salinities. 
These dependencies (the case of \emph{open system}) are represented by solid lines. 
For example, the blue solid line illustrates the compression (or swelling) of the gel in equilibrium with a reservoir of salinity, $\cs=0.063$ mol/l. 
The points where the pressure equals zero, $\Pgel=0$, (indicated by filled circles) are the gel \emph{free swelling equilibrium} states. 
These states shift towards smaller volumes with increase of salinity. 
In general, the increase of salinity shift all the $\Pgel(V)$ curves towards smaller volumes.
This effect is well known and is typical for all branched \emph{strong} polyelectrolytes. 
It is caused by the decrease of ions osmotic pressure and by a screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.
\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.}

@@

\paragraph{Compression in closed system.}
Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
These states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the amount of ions in gel \{$\Nna^0$, $\Ncl^0$\} 
(Index ``0'' stands for zero bar applied pressure).
We use the free swelling equilibrium states as the starting ones for the gel compression in \emph{closed system}. 
Thus, we simulate the compression of the gel in a closed volume, $\Vbox$, which is equal to $\Vgel^0$, and contains $\Ncl^0$ of $\cl$ ions and the $\na$ ions in the amount neutralizing the system, $\Nna^0 = $$\Ncl^0 + \Ngel$.

@@

The processes of the gel compression in \emph{closed} system are depicted in Figure~\ref{fig: PV} as dotted lines.
In this plot, the blue dotted line, for example, illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l, in a volume which gel has at zero pressure. 
Since, in this case, the volumes of the gel $\Vgel$ and of the supernate $\Vout$ are comparable, the compression of the gel affects the salinity of supernate, $\cs$. 
The supernate salinity now decreases with compression.
This decrease is illustrated \reffig{fig: CV}, where the same swelling/compression processes are displayed in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
In these coordinates, all the open system compressions show up as horizontal lines, which reflects the constant salinity, whereas the compressions in closed system demonstrate the change of $\cs$ from $\cs^{0}=0.063$ at zero pressure $\Pgel$ to $\cs^{5}=0.045$ mol/l at $P\gel=5$ bar (index ``5'' stands for 5 bar).

Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, \ie in the volume where the gel is compressed (or swells), changes.
%As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \Vgel^0$.
In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
The depicted value can be considered as the density of $\cl$ ions averaged out over the volume $\Vbox$.

As it is expected in case of closed system these dependencies look like horizontal lines, whereas in open system, the amount of ions in compression volume increases with compression. 
This implies, that the compression of the gel in open system pulls out the ions from the bath to the compression volume, $\Vbox$. 
And vice versa, the swelling of the gel pushes ions out to the bath.

@@

\paragraph{Desalination scheme.}
As we have seen, the compression of the gel in a closed system affects the salinity, whereas the compression in an open system affects the amount of ions in a volume where the gel is compressed in. 
Here we show how to employ these phenomena for water desalination. 
The highlighted colored lines on plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} form a sequence of the following one by each other swellings and compressions of the hydrogel, correspondingly in \emph{open} and \emph{closed} systems. 
This sequence forms the water desalination process.
Starting from swelling the gel in the \emph{open} system at high salinity ($\cs=0.091$ mol/l, solid black line), the gel gets compressed in \emph{closed} system until the pressure reaches 5 bar (dashed black line). 
Then the same gel swells in a reservoir of a bit lower salinity (\ie $\cs=0.064$ mol/l, light blue line). 
After swelling, the gel is compressed again by the pressure of 5 bar in \emph{closed} system (dashed light blue line).  
Then it is put swelling in a reservoir of even smaller salinity ($\cs=0.045$ mol/l, solid yellow line). 
And so on. 
The chain of alternating swelling and compression steps ends up when salinity gets equal to $\cs=4\cdot10^{-3}$ mol/l after compression in closed system (dashed magenta line).

@@

\paragraph{The efficiency of desalination.}
The theoretical minimum specific energy for seawater desalination ($\cs=35$ g/l, $\simeq0.6$ mol/l as for pure NaCl) is 1.1 kWh/m3 (3.9 kJ/L) for 50\% recovery \cite{Wang_2020}.
This value is calculated as follows 
\begin{equation}
W=2RT\left(\frac{c_{f}}{R_{w}}\ln\frac{c_{b}}{c_{f}}-c_{p}\ln\frac{c_{b}}{c_{p}}\right)
\label{eq:SEC}
\end{equation}
where $R$ is a universal gas constant, $c_{f}$ is the salinity of feed water, $c_p$~--- of product water and $c_b$~--- the salinity of the brine, which necessarily appears in any desalination process. 
$R_{w}$ is a recovery ratio, \ie the ratio between volume of produced water and the volume of the feed water. 
50\% recovery ratio means that one part of feed water divides into two equal volume solutions of the product water and of the brine.
Of course, a significant amount of additional energy is required to operate the system\cite{Kim_2019}. 
It has been reported that the specific energy consumption (SEC) of reverse osmosis (RO) process is 2.5~-- 4.0 kWh/m3 (9~-- 14.4 kJ/l), which is significantly higher than its minimum specific energy.
The SEC of a real-scale RO plant is even higher, approximately 3.5~-- 4.5 kWh/$m^{3}$ (12.6 - 16.2 kJ/L), including pre-treatment and post-treatment processes \cite{Kim_2018}. 
%Because of the inherent high energy requirement for RO desalination, seawater is not commonly utilized over traditional surface water.

In order to compare the efficiency of the process presented in \ref{fig: PV and CV} and \ref{fig: NV and CN} with provided values we collect the corresponding data to the Table~\ref{tab: table}.
The presented desalination process is a cascade of six swellings in open system, at six different (constant) salinities $\cs$, each followed by six compressions in closed system, at six different (constant) $\ncl$.
Each swelling and compression presented as a row of the Table~\ref{tab: table}, which is collored to matching to the lines on Figures.
The first column of the table contains values $\cs^0$ and $\cs^5$, which stand for the supernatant salinity at 0 and 5 bar compression; in open system supernatant salinity does not change, so $\cs^0$ and $\cs^5$ are presented by a single number. 
The second column contains values of $n^0$ and $n^5$, which stand for the number of $\cl$ ions in compression volume at 0 and 5 bar pressure. \todo[fancyline]{it is not a number but a number in unit volume}
The number of ion does not change in closed system compression, thus $n^0$ and $n^5$ are the same in corresponding row.
The fourth column shows the change of the volume in corresponding process, $\Delta v$. 
The fifth column contain the work needed for the compression in the corresponding process, calculated per volume of extracted solution. 
This value is calculated as integral of corresponding $\Pgel(\Vgel)$ dependence
\begin{equation}
    W = \frac{\int_{v^0}^{v^5} \Pgel d\Vgel}{\Delta v}
\end{equation}
Here, in the table we present the absolute value, whereas one should keep in mind that the compression implies the work which is done by external force, whereas the swelling implies the work which is done by gel.
\todo{may be we return back the 'minuses' to the W values}

@@

@@

\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$95.4\pm1.86$}} &  & \multirow{2}{*}{}\tabularnewline
 &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}

@@

@@

\multicolumn{2}{l|}{{\small{}$89.41\pm0.229\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}$109.1\pm1.72$}} &  & \multirow{2}{*}{}\tabularnewline
\multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  &  & \tabularnewline
\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.083\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}0.54}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.69$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.58\pm0.013$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}

@@

@@

\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.37$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.016$}} &  &  &  &  &  &  & \tabularnewline
\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.057\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}0.53}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.51$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.91\pm0.010$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}

@@

@@

\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.13$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.80\pm0.008$}} &  &  &  &  &  &  & \tabularnewline
\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.037\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}0.52}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.42$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.30\pm0.006$}} &  &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}

@@

@@

@@

@@

@@

@@

@@

@@

\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.064\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.77$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.08\pm0.002$}} &  &  &  &  &  &  & \tabularnewline
\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}0.55}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.05$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.01$\pm$0.002}} &  &  &  &  & \tabularnewline
\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.046\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm0.97$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.86\pm0.001$}} &  &  &  &  &  &  & \tabularnewline

@@

\caption{All the units calculated per one mol of gel segments. Values in brackets
are the estimates corresponding to crossection of 'red' and 'orange'
lines on the plots of figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
}
\end{table}

>>>>

%Let $\nna$ and $\ncl$ be the density of the corresponding ion in the compression volume, $\Vbox$ averaged over this volume
\begin{equation}
N_i = N_i\gel + \cs\cdot(\Vbox - \Vgel)
\end{equation}
where $i \in \{\na, \cl\}$,  $N_i$ is the amount of the corresponding ions in gel, $\Vgel$~--- volume of the gel, $\Vbox$~--- the volume in which the gel is compressed. As $\Vbox$ we choose the volume of the gel in the free swelling equilibrium state.

@@

\paragraph{Closed system.}
The similar scheme we use to simulate the gel in closed system. 
The procedure represents a chain of subsequent MD and MC simulation, but now the molecular dynamics is running in two simulation boxes simultaneously.
The first box of the volume $\Vgel$ contains the gel with ions, and the second box, $\Vout$--- contains only ions. 
The total volume of both boxes is kept constant, $\Vbox=V_{\mathrm{gel}}+V_{\mathrm{out}}$, so the compression of the gel implies the decreasing $\Vgel$ and increasing $\Vout$.
These two boxes are represented in \reffig{fig:diamond}.

\paragraph{Algorithm.}
The thermodynamic equilibrium between the two volumes implies the exchange of ion pairs between them, which is done by means of MC procedure in a way similar to described in \cite{Panagiotopoulos1988b}.
The simulation algorithm is following:
\begin{enumerate}
\item Simulate molecular dynamics in both boxes; collect the observables, for example, values of pressure $P$, to an array; 
\item Perform Monte-Carlo procedure simulating ion pair exchange; collect the arrays of observables samples: number of ions in both boxes, 
%$\nna\gel$,
$\Ncl\gel$ 
%$\nna\out$ 
and $\Ncl\out$ ; 
\item Repeat the procedure until the desired length of sample arrays is reached.
\end{enumerate}

@@

The dependencies of $\Pgel$ on the gel molar volume $\Vgel$ are present in Figure \ref{fig: PV} for a set of different salinities. \todo{consider treplacing $\Pgel$ by $\Pi$}
These dependencies (the case of \emph{open system}) are represented by solid lines. 
For example, the blue solid line illustrates the compression (or swelling) of the gel in equilibrium with a reservoir of salinity, $\cs=0.063$ mol/l. 
The points where the pressure equals zero, $\Pgel=0$, (indicated by filled circles) are the gel \emph{free swelling equilibrium} states. 
These states shift towards smaller volumes with increase of salinity. 
In general, the increase of salinity shift all the $\Pgel(V)$ curves towards smaller volumes.
This effect is well known and is typical for all branched \emph{strong} polyelectrolytes. 
It is caused by the decrease of ions osmotic pressure and by a screening of electrostatic interactions \cite{Zhulina2000, Landsgesel2020a}.
\footnote{The salinity dependence of the size of \emph{weak} polyelectrolyte gel is in general non-monotonic. We discuss this case in \cite{Rud2018}.}

@@

\paragraph{Compression in closed system.}
%Each set of simulations in \emph{open system} defines the free swelling equilibrium states of the gel for each salinity, \ie the state where the gel partial pressure equals zero. 
The free swelling equilibrium states are characterized by the corresponding molar volume of the gel, $\Vgel^0$ and the amount of ions in gel \{$\Nna^0$, $\Ncl^0$\} 
(Index ``0'' stands for zero bar applied pressure).
We use these states as the starting ones for the gel compression in \emph{closed system}. 
Thus, we simulate the compression of the gel in a closed volume, $\Vbox$, which is equal to $\Vgel^0$, and contains $\Ncl^0$ of $\cl$ ions and the $\na$ ions in the amount neutralizing the system, $\Nna^0 = $$\Ncl^0 + \Ngel$.

@@

The processes of the gel compression in \emph{closed} system are depicted in Figure~\ref{fig: PV} as dotted lines.
In this plot, the blue dotted line, for example, illustrates the compression of the gel equilibrated with the solution of salinity $\cs=0.063$ mol/l, in a volume which gel has at zero pressure. 
Since, in this case, the volumes of the gel $\Vgel$ and of the supernate $\Vout$ are comparable, the compression of the gel decreases the salinity of supernate, $\cs$. 
%The supernate salinity now decreases with compression.
This dependence is illustrated \reffig{fig: CV}, where the same swelling/compression processes are displayed in different coordinates: \ie salinity of supernate versus the gel molar volume, $\cs(\Vgel)$.
In these coordinates, all the open system compressions show up as horizontal lines, which reflects the constant salinity, whereas the compressions in closed system demonstrate the change of $\cs$ from $\cs^{0}=0.063$ at zero pressure $\Pgel$ to $\cs^{5}=0.045$ mol/l at $P\gel=5$ bar (index ``5'' stands for 5 bar).

Although the salinity during compression in \emph{open} system remains constant, the number of ions in a compression volume, \ie in the volume where the gel is compressed (or swells), changes.
%As the compression volume $\Vbox$ we chose the volume of the free swelling equilibrium state of the gel, $\Vbox = \Vgel^0$.
In the Figure \ref{fig: NV} we depicted the number of $\cl$ ions in the volume $\Vbox$, calculated per unit volume, $\ncl =$ $\Ncl/\Vbox$, as a function of the gel molar volume. 
The depicted value can be considered as the density of $\cl$ ions averaged out over the compression volume $\Vbox$.

As expected in the case of closed system compression these dependencies look like horizontal lines, whereas in an open system, the amount of ions in compression volume increases with compression. 
This implies, that the compression of the gel in the open system pulls out the ions from the bath to the compression volume, $\Vbox$. 
And vice versa, the swelling of the gel pushes ions out to the bath.

@@

\paragraph{Desalination scheme.}
As we have seen, the compression of the gel in a closed system affects the salinity, whereas the compression in an open system affects the amount of ions in a volume where the gel is compressed in. 
Here we show how to employ these phenomena for water desalination. 
The highlighted colored lines on plots of Figures \ref{fig: PV and CV} and \ref{fig: NV and CN} form a sequence of the following one by each other swellings and compressions of the hydrogel, correspondingly in \emph{open} and \emph{closed} systems. 
This sequence forms the water desalination process.
Starting from swelling the gel in the \emph{open} system at high salinity ($\cs=0.091$ mol/l, solid black line), the gel gets compressed in \emph{closed} system until the pressure reaches 5 bar (dashed black line). 
Then the same gel swells in a reservoir of a bit lower salinity (\ie $\cs=0.064$ mol/l, light blue line). 
After swelling, the gel is compressed again by the pressure of 5 bar in \emph{closed} system (dashed light blue line).  
Then the gel is put swelling in a reservoir of even smaller salinity ($\cs=0.045$ mol/l, solid yellow line). 
And so on. 
The chain of alternating swelling and compression steps ends up when salinity gets equal to $\cs=4\cdot10^{-3}$ mol/l after compression in closed system (dashed magenta line).

@@

\paragraph{The efficiency of desalination.}
The theoretical minimum specific energy for seawater desalination (
%$\cs=35$ g/l, 
$\cs\simeq0.6$ mol/l as for pure NaCl) is $\sim3.9$ kJ/l (1.1 kWh/m$^3$) for 50\% recovery \cite{Wang_2020}.
This value is calculated as follows 
\begin{equation}
W=2RT\left(\frac{c_{f}}{R_{w}}\ln\frac{c_{b}}{c_{f}}-c_{p}\ln\frac{c_{b}}{c_{p}}\right)
\label{eq:SEC}
\end{equation}
where $R$ is a universal gas constant, $c_{f}$ is the salinity of feed water, $c_p$~--- of product water and $c_b$~--- the salinity of the brine, which necessarily appears in any desalination process. 
$R_{w}$ is a recovery ratio, \ie the ratio between volume of produced water and the volume of the feed water. 
50\% recovery ratio means that one part of feed water divides into two equal volume solutions of the product water and of the brine.
Of course, a significant amount of additional energy is required to operate the system\cite{Kim_2019}. 
It has been reported that the specific energy consumption (SEC) of reverse osmosis (RO) process is 2.5~-- 4.0 kWh/m3 (9~-- 14.4 kJ/l), which is significantly higher than its minimum specific energy.
The SEC of a real-scale RO plant is even higher, approximately 3.5~-- 4.5 kWh/$m^{3}$ (12.6 - 16.2 kJ/L), including pre-treatment and post-treatment processes \cite{Kim_2018}. 
%Because of the inherent high energy requirement for RO desalination, seawater is not commonly utilized over traditional surface water.

In order to compare the efficiency of the process presented in \ref{fig: PV and CV} and \ref{fig: NV and CN} with provided values, we collect the corresponding data to the Table~\ref{tab: table}.
The presented desalination process is a cascade of six swellings in open system, at six different (constant) salinities $\cs$, each followed by six compressions in closed system, at six different (constant) $\ncl$.
Each swelling and compression process is presented as a row of Table~\ref{tab: table}, which is colored by matching the lines in the Figures.
The first column of the table contains values $\cs^0$ and $\cs^5$, which stand for the supernate salinity at 0 and 5 bar compression; in open system, supernate salinity does not change, so $\cs^0$ and $\cs^5$ are presented by a single number. 
The second column contains values of $n^0$ and $n^5$, which stand for the number of $\cl$ ions in compression volume $\Vbox$, at 0 and 5 bar pressure (divided by $\Vbox$). 
The number of ion does not change in closed system compression, thus $n^0$ and $n^5$ are the same in the corresponding rows.
The third column shows the change of the gel volume in corresponding process, $\Delta v$. 
The fourth column contain the work needed for the compression in the corresponding process, calculated per volume of extracted solution. 
This value is an integral of corresponding $\Pgel(\Vgel)$ dependence
\begin{equation}
    W = \frac{\int_{v^0}^{v^5} \Pgel d\Vgel}{\Delta v}
\end{equation}
Here, in the table, we present the absolute values of the work, whereas one should keep in mind that the compression implies the work is done by external force and the swelling implies that the work is done by gel.

@@

\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}ll|lc|c|l|ll}
\multicolumn{1}{l|}{$c_{s}^{0}$, mM} & $c_{s}^{5}$, mM & \multicolumn{1}{l|}{$n_{\cl}^{0}$, mM} & $n_{\cl}^{5}$, mM & $\Delta v$, l & $|W$\textbar , J/L & \multicolumn{2}{c}{$W^{id}$, J/L}\tabularnewline

@@

\multirow{2}{*}{{\small{}$91.47$}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{{\small{}$57.08\pm0.122\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}2.74}} & \multirow{2}{*}{{\small{}$95.4\pm1.86$}} &  & \multirow{2}{*}{}\tabularnewline
 &  & \multicolumn{2}{r|}{{\small{}$71.75\pm0.024$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{teal}{\small{}$\left.\begin{array}{l}

@@

\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}{\color{teal}\ensuremath{\begin{array}{cc}
W^{\mathrm{sim}}= & 202.8\pm3.23\\
W^{id}= & 52.9\\

@@

\end{array}}}}$}} & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{{\small{}$89.41\pm0.229\enskip\longrightarrow$}} & \multirow{2}{*}{{\small{}56.90}} & \multirow{2}{*}{} & \multirow{2}{*}{{\small{}2.72}} & \multirow{2}{*}{{\small{}$109.1\pm1.72$}} &  & \multirow{2}{*}{}\tabularnewline
\multicolumn{2}{r|}{{\small{}$73.63\pm0.03$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multirow{2}{*}{\textcolor{teal}{\small{}63.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{teal}{\small{}$37.28\pm0.083\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}3.26}} & \multirow{2}{*}{\textcolor{teal}{\small{}$100.9\pm1.69$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{teal}{\small{}$50.58\pm0.013$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{olive}{\small{}$\left.\begin{array}{l}

@@

\end{array}\right\rbrace $$\rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
W^{\mathrm{sim}}= & 207.3\pm2.19\\

@@

\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{\textcolor{teal}{\small{}$62.05\pm0.15\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{teal}{\small{}37.17}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{teal}{\small{}3.18}} & \multirow{2}{*}{\textcolor{teal}{\small{}$107.4\pm1.37$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{teal}{\small{}$48.21\pm0.016$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multirow{2}{*}{\textcolor{olive}{\small{}44.91}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{olive}{\small{}$23.75\pm0.057\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}3.82}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.7\pm1.51$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{olive}{\small{}$35.91\pm0.010$}} &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{red}{\small{}$\left.\begin{array}{l}

@@

\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
W^{\mathrm{sim}}= & 222.3\pm2.43\\
W^{\mathrm{id}}= & 43.8\ {\color{red}{\scriptstyle (41.0)}}\\

@@

\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{\textcolor{olive}{\small{}$43.46\pm0.12\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{olive}{\small{}24.27}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{olive}{\small{}3.91}} & \multirow{2}{*}{\textcolor{olive}{\small{}$106.4\pm1.13$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{olive}{\small{}$30.80\pm0.008$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multirow{2}{*}{\textcolor{red}{\small{}31.93}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{red}{\small{}$14.66\pm0.037\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{red}{\small{}4.20}} & \multirow{2}{*}{\textcolor{red}{\small{}$107.9\pm1.42$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{red}{\small{}$25.30\pm0.006$}} &  &  &  & \multirow{8}{*}{{\small{}\hspace{-1em}}\textcolor{orange}{\small{}$\left.\begin{array}{l}

@@

\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
W^{\mathrm{sim}}= & 218.7\pm2.19\\

@@

\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 

@@

\end{array}$}} & \multirow{2}{*}{\textcolor{red}{\small{}$\begin{array}{c}

@@

\end{array}$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 

@@

\end{array}$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$\begin{array}{c}

@@

\end{array}$}} &  &  & \multirow{7}{*}{{\small{}\hspace{-1em}}\textcolor{magenta}{\small{}$\left.\begin{array}{l}

@@

\end{array}\right\rbrace \rotatebox{90}{\hspace{-5em}\ensuremath{\begin{array}{cc}
W^{\mathrm{sim}}= & 227.5\pm2.23\\

@@

\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{\textcolor{orange}{\small{}$20.74\pm0.064\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{orange}{\small{}8.83}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{orange}{\small{}$4.71$}} & \multirow{2}{*}{\textcolor{orange}{\small{}$110.8\pm0.77$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{orange}{\small{}$11.08\pm0.002$}} &  &  &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multirow{2}{*}{\textcolor{magenta}{\small{}10.90}} & \multirow{2}{*}{} & \multicolumn{2}{l|}{\textcolor{magenta}{\small{}$3.00\pm0.01\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}6.08}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$106.9\pm1.05$}} &  & \tabularnewline
 &  & \multicolumn{2}{r|}{\textcolor{magenta}{\small{}9.01$\pm$0.002}} &  &  &  & \tabularnewline
\cline{1-6} \cline{2-6} \cline{3-6} \cline{4-6} \cline{5-6} \cline{6-6} 
\multicolumn{2}{l|}{\textcolor{magenta}{\small{}$9.83\pm0.046\enskip\longrightarrow$}} & \multirow{2}{*}{\textcolor{magenta}{\small{}3.12}} & \multirow{2}{*}{} & \multirow{2}{*}{\textcolor{magenta}{\small{}5.78}} & \multirow{2}{*}{\textcolor{magenta}{\small{}$119.4\pm0.97$}} &  & \tabularnewline
\multicolumn{2}{r|}{\textcolor{magenta}{\small{}$3.86\pm0.001$}} &  &  &  &  &  & \tabularnewline

@@

\caption{The estimates of the efficiency of the desalination process. All the units are calculated per one mol of gel segments. Values in brackets
are the estimates corresponding to crossection of 'red' and 'orange' lines on the plots of figures \ref{fig: PV and CV} and \ref{fig: NV and CN}
}
\end{table}
